High-Fidelity Counterfactual Explanations through Conformal Prediction

### 2023-05-08 notebooks/mnist.qmd
code for tables mostly sorted

```{julia}
Random.seed!(2023)

@@

```{julia}
# Search:
generic_generator = GenericGenerator(opt=Flux.Optimise.Descent(1.0))
ce_wachter = generate_counterfactual(
    x_factual, target, counterfactual_data, M, generic_generator; 
    decision_threshold=γ, max_iter=T,
    initialization=:identity,
)
greedy_generator = GreedyGenerator(η=2.0)
ce_jsma = generate_counterfactual(
    x_factual, target, counterfactual_data, M, greedy_generator; 
    decision_threshold=γ, max_iter=T,
    initialization=:identity,
)
```

>>>>

```{julia}
Random.seed!(1234)

@@

```{julia}
# Search:
generic_generator = GenericGenerator(opt=Flux.Optimise.Adam(1.0))
ce_wachter = generate_counterfactual(
    x_factual, target, counterfactual_data, M, generic_generator; 
    decision_threshold=γ, max_iter=T,
    initialization=:identity,
)
greedy_generator = GreedyGenerator(η=2.0)
ce_jsma = generate_counterfactual(
    x_factual, target, counterfactual_data, M, greedy_generator; 
    decision_threshold=γ, max_iter=T,
    initialization=:identity,
)
```
